---
title: "P8105 Homework 6"
author: "Junhui Mi"
date: "2019/11/24"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%")

library(tidyverse)
library(ggridges)
library(modelr)
library(mgcv)

set.seed(1)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

### Load and clean the data
```{r}
birthweight = read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(babysex = factor(babysex, levels = c(1,2), labels = c("male", "female")),
         frace = factor(frace, levels = c(1,2,3,4,8,9), labels = c("white", "black", "asian", "puerto_rican", "other", "unknown")),
         malform = factor(malform, levels = c(0,1), labels = c("absent", "present")),
         mrace = factor(mrace, levels = c(1,2,3,4,8), labels = c("white", "black", "asian", "puerto_rican", "other")))

skimr::skim(birthweight)
```

The dataset contains 20 variables and 4342 observations. There is no missing data.

### Propose a regression model

Bulid the model on a data-driven model-building process: First I put all variables in my linear regression model.  

```{r}
birthweight %>%
  lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Using significance level alpha = 0.05, I choose variables with p-value < 0.05 and fit them in my model. 

In my model, birthweight is associated with baby’s sex, baby’s head circumference at birth, baby’s length at birth, mother’s weight at delivery, gestational age, mother’s race, number of live births prior to this pregnancy, and mother's average number of cigarettes smoked per day during pregnancy.

```{r}
my_model = birthweight %>%
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + parity + smoken, data = .)

birthweight %>%
  modelr::add_predictions(my_model) %>%
  modelr::add_residuals(my_model) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() + geom_smooth(method = lm) +
  labs(x = "Fitted values",
       y = "Residuals",
       title = "Plot of model residuals against fitted values")
```

Above is a plot of my model residuals against fitted values.

### Compare my model with other two model

```{r}
model_1 = birthweight %>%
  lm(bwt ~ blength + gaweeks, data = .)

model_2 = birthweight %>%
  lm(bwt ~ babysex * bhead * blength, data = .)

cv_df = 
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
    ) %>%
  mutate(
    my_model = map(train, ~ lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + parity + smoken, data = .x)),
    model_1 = map(train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
    model_2 = map(train, ~ lm(bwt ~ babysex * bhead * blength, data = .x))
    ) %>% 
  mutate(
    rmse_my_model = map2_dbl(my_model, test, ~ rmse(model = .x, data = .y)),
    rmse_model_1 = map2_dbl(model_1, test, ~ rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~ rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()  +
  labs(title = "Prediction errors in different models")
```

From the plot above we can see that my model has the least RMSE. My model is the best among three models, model_2 ranks second and model_1 ranks third.

# Problem 2

### Load data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Bootstrap
```{r}
weather_bootstrap = weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results_1 = map(models, broom::glance),
    results_2 = map(models, broom::tidy),
    r_squared = map_dbl(.x = results_1, ~.x %>% pull(r.squared)),
    log_b0_b1 = map_dbl(.x = results_2, ~.x %>% pull(estimate) %>% prod %>% log)) %>%
  select(.id, r_squared, log_b0_b1)
```

### Distribution of two estimated quantities
```{r}
weather_bootstrap %>%
  ggplot(aes(x = r_squared)) + geom_density() +
  labs(x = expression(""~r^2~""),
       title = expression("Distribution of "~r^2~""))

weather_bootstrap %>%
  ggplot(aes(x = log_b0_b1)) + geom_density() +
  labs(x = expression("log("~hat(beta)[0]~"*"~hat(beta)[1]~")"),
       title = expression("Distribution of log("~hat(beta)[0]~"*"~hat(beta)[1]~")"))
```

The distribution of r_squared is a little left-skewed normal with mean around 0.91, and the distribution of log_b0_b1 is a little left-skewed  normal with mean around 2.02.

### Confidence Interval of estimates
```{r}
weather_bootstrap %>%
  pivot_longer(
    -.id,
    names_to = "estimates",
    values_to = "value"
    ) %>%
  group_by(estimates) %>%
  summarize(quantile2.5 = round(quantile(value,0.025), digits = 3),
            quantile97.5 = round(quantile(value,0.975), digits = 3)) %>%
  mutate(CI = str_c(quantile2.5, quantile97.5, sep = ",")) %>%
  knitr::kable(caption = "95% CI of estimates", format = "html", digits = 3)
```

The 95% confidence interval of log_b0_b1 is (1.966,2.058), and (0.894,0.927) for r_squared.