---
title: "P8105 Homework 6"
author: "Junhui Mi"
date: "2019/11/9"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%")

library(tidyverse)
library(ggridges)

set.seed(1)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

### Load and clean the data
```{r}
birthweight = read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(babysex = factor(babysex, levels = c(1,2), labels = c("male", "female")),
         frace = factor(frace, levels = c(1,2,3,4,8,9), labels = c("white", "black", "asian", "puerto_rican", "other", "unknown")),
         malform = factor(malform, levels = c(0,1), labels = c("absent", "present")),
         mrace = factor(mrace, levels = c(1,2,3,4,8), labels = c("white", "black", "asian", "puerto_rican", "other")))

skimr::skim(birthweight)
```

The dataset contains 20 variables and 4342 observations. There is no missing data.

### Propose a regression model

Bulid the model on a data-driven model-building process: First I put all the variables in my linear regression model.

```{r}
birthweight %>%
  lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Using significance level alpha = 0.05, I choose variables with p-value < 0.05 and fit them in my model.

```{r}
my_model = birthweight %>%
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + parity + smoken, data = .)

birthweight %>%
  modelr::add_predictions(my_model) %>%
  modelr::add_residuals(my_model) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() + geom_smooth(method = lm) +
  labs(x = "Fitted values",
       y = "Residuals",
       title = "Plot of model residuals against fitted values")
```

### Compare my model with other two model

```{r}
model_1 = birthweight %>%
  lm(bwt ~ blength + gaweeks, data = .)

model_2 = birthweight %>%
  lm(bwt ~ babysex * bhead * blength, data = .)
```

# Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())


```
